\thetitle

### 2021-03-01 writing/results.tex
cleaning up prose

>>>>

At this point all ingredients are in place to describe the first application of
the evaluation method. Two things are needed: (1) the description of the
experimental setup, including the experimental questions; and (2) a set of
representative benchmark programs. The first two subsections address these
issues in order. The last one presents the observed results.

### 2021-03-01 writing/sample.tex
Lots of minor changes and rewordings
organize sections/titles/labels in paper
cleaning up prose

\section{How to Sample the Experimental Space}

The mutators from section~\ref{sec:mutate} generate 96,515,744 debugging
scenarios; far too many to even identify the interesting ones among them.
Furthermore this population is heterogeneous; different scenarios come
from different mutants and different mutants are the result of a
different mutator and benchmark pair. Hence, to make the experiment
computationally feasible and statistically precise, we perform stratified
uniform random sampling with three levels of stratification.  The first
two levels of strata group mutants first by benchmark and then by mutator. 
We randomly select from the mutants of
each benchmark ensuring that, per
benchmark, the sample reflects the diversity of mutants with respect to
the mutators that generated them.  Specifically,  we sample 80 mutants
with interesting scenarios per benchmark,  evenly-distributed across all
of the mutators that contribute mutants for the benchmark.  The third
level of strata for our sampling is the lattice of a single mutant and we draw 96 random
interesting scenarios from each lattice with replacement.

In summary, our sampling process takes advantage of ancillary information
to deliver a  sufficiently large representative set of scenarios.
Concretely, we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore, stratified random sampling allows us to derive precise conclusions
about the proportion of the whole population that satisfies a given trait 
from the sample despite the population's heterogeneity.
That property is exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to the set of all interesting debugging
scenarios.

>>>>

%% -----------------------------------------------------------------------------

%  from section~\ref{sec:mutate} (96,515,744)

As is, the chosen mutators generate a huge number of debugging scenarios,
approximately 1,000,000 for a suitable benchmark suite such as the one used for
the first experiment (see~sec.~\ref{sub:results-benchmarks}). This number of
scenarios is far too large to even identify the interesting ones among them.
Furthermore this population is heterogeneous; different scenarios come from
different mutants and different mutants are the result of a different mutator
and benchmark pair.

To make the experiment computationally feasible and statistically precise,
stratified uniform random sampling with three levels of stratification becomes
necessary.  The first two levels group mutants first by benchmark and then by
mutator.  The set of randomly select from the mutants of each benchmark is
checked to make sure that, per benchmark, the sample reflects the diversity of
mutants with respect to the mutators that generated them.  Specifically, the
process samples 80 mutants with interesting scenarios per benchmark,
evenly-distributed across all of the mutators that contribute mutants for the
benchmark.  At the third level, the sampling process draws 96 random interesting
scenarios from each configuration lattice with replacement.

%% This looks like a repeat of the above, made concrete for the benchmark set

% In summary, the sampling process takes advantage of ancillary information to
% deliver a sufficiently large representative set of scenarios.  Concretely, we
% test each mode of the rational programmer on 72,192 randomly selected
% interesting debugging scenarios spread across both benchmarks and mutators.
% Furthermore, stratified random sampling allows us to derive precise conclusions
% about the proportion of the whole population that satisfies a given trait from
% the sample despite the population's heterogeneity.  That property is exactly
% what we need to project comparisons about the usefulness of various modes of the
% rational programmer from the sample to the set of all interesting debugging
% scenarios.
